Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-31 rnni_convexity.tex
delete notation for cherries

The path $p$ returned by $\csort$ is a shortest caterpillar path because every tree modification on $p$ reduces the number of inversions of taxa in $T$ and $R$.
Indeed, no $\rnni$ move on caterpillar trees can reduce the number of taxa inversions by more than one, assuming that inversions with both taxa of a cherry are counted only once, that is, if both pairs of taxa $(x, z)$ and $(y, z)$ appear in opposite orders in $T$ and $R$ and $(x,y)$ is a cherry then they are counted as one inversion.
Hence any caterpillar path every move along which reduced the number of inversions is a shortest caterpillar path.

>>>>

The path $p$ returned by $\csort$ is a shortest caterpillar path because every tree modification on $p$ reduces the number of inversions of taxa in $T$ and $R$.
Indeed, no $\rnni$ move on caterpillar trees can reduce the number of taxa inversions by more than one, assuming that inversions with both taxa of a cherry are counted only once, that is, if both pairs of taxa $(x, z)$ and $(y, z)$ appear in opposite orders in $T$ and $R$ and $x$ an $y$ build a cherry then they are counted as one inversion.
Hence any caterpillar path every move along which reduced the number of inversions is a shortest caterpillar path.
